Presentation Title

### 2017-07-18 thesis/chapters/ch3-model.tex
Write synchroniser

\subsection{Relationship with $\alpha$-synchroniser}
TODO

@@

\subsection{Use epidemic protocol instead of broadcast protocol}
One of the final steps in our consensus protocol is to broadcast the consensus result and signatures to every other node (\Cref{sec:consensus-phase}).
While this guarantees delivery (since we assumed reliable channel), it is wasteful.
For example, if every facilitator is honest, a node would receive $n$ consensus results which are identical when only one is necessary.

>>>>

Our protocol has some similarities with synchronisers~\cite[Chapter 10]{podc} because it is effectively a technique to introduce synchrony in an asynchronous environment.
If we consider the facilitators is a collective authority, then it can be seen as a synchroniser that sends pulse messages (in the form of \texttt{cons\_msg} and \texttt{cons\_sig}) to indicate the start of a new clock pulse.
Every node then sends a completion messages (in the form of \texttt{cp\_msg}) to the collective authority to indicate that they are ready to start a new pulse.

@@

\subsection{Using epidemic protocol to reduce communication cost}
One of the final steps in our consensus protocol is to broadcast the consensus result and signatures to every other node (\Cref{sec:consensus-phase}).
While this guarantees delivery (since we assumed reliable channel), it is wasteful.
For example, if every facilitator is honest, a node would receive $n$ consensus results which are identical when only one is necessary.
